Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
conclusion

To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
  \sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square represents the
statistical significance of the diagnostic accuracy amongst the different techniques, i.e.,
if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different.

\begin{figure}[h]
	\vspace{-1.2cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
\end{figure}

@@

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k}, 
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.

Future work is as follows:

>>>>

To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
  \sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square represents the
statistical significance of the diagnostic accuracy amongst the different techniques, i.e.,
if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different. As the results
are statiscally significant, we can confirm that \ds{} improves \sfl{}.

\begin{figure}[h]
	\vspace{-1cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
\end{figure}

@@

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. \ds{} is This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k}, 
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.

Future work is as follows: improve our oracle heuristics to handle more exceptions;
conduct experiments in more \dfj{} faults or other datasets; find techniques to
handle the cases which harm the cost of diagnosis, such as, faults of omission,
test design problems and the cases which the buggy-class is not in the top-$k$ of 
highest-rank faulty classes.
